\cvsection[column2]{Education}

\cvevent{PhD in Telematic Systems Engineering}{Universidad Politécnica de Madrid}{2020 -- Actualidad}{Madrid}

\cvevent{MSc in Telecommunications Engineering {\small(Mean 9.5, Honors in 10 subjects)}}{Universidad Politécnica de Madrid}{2018 -- 2020}{Madrid}
\cvevent{BSc in Telecommunications Technologies and Services Engineering {\small(Mean 8.8, \nth{1} in telematics specialization, Honors in 21 subjects)}}{Universidad Politécnica de Madrid}{2014 -- 2018}{Madrid}

%%\cvevent{Bachillerato científico-tecnológico %%\textit{\small(Media 10, 1º de la promoción)}}{IES Eduardo %%Blanco Amor}{2012 -- 2014}{Ourense}

\divider

\cvsection{Professional experience}

\cvevent{Next Generation Internet Group}{Telematic Systems Engineering Department, UPM}{Jan 2020 -- Nowadays}{Madrid}
\begin{itemize}
\item Participation in European projects in the area of Linked Open Data, Machine Learning and Digital Twins.
\item FIWARE contributor: The Open Source Platform for Our Smart Digital Future.
\end{itemize}
\divider

\cvevent{Teaching collaborations}{UPM}{Jan 2019 -- Nowadays}{Madrid}
\begin{itemize}
\item Master's and Bachelor's Thesis supervisor.   
\end{itemize}
\divider

\cvevent{ETSIT's Digital Integration}{Ángel Barbero Martín de Vidales' Foundation}{March 2018 -- July 2020}{Madrid}
\begin{itemize}
\item Development and operation of University's web applications.
\item Management of IT infrastructure. 
\item Designing, maintenance and consumption of databases.
\end{itemize}
\divider

\cvevent{SENER Ingeniería y Construcción}{
University scholarship}{Jan 2018 -- March 2018}{Madrid}
\begin{itemize}
\item Aerospace sector.
\item Development of a service for data consumption and failure detection from measuring machines. 
\end{itemize}
\divider

\clearpage